timesliced_random_cell_selection

### 2018-12-13 src/timesliced_random_cell_selection.Rmd
someone turned off pc... blocking code

First you need to put the background (background_all) into a spatialpointsdataframe.
```{r}
xy <- background_all[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude
background_all_sp <- SpatialPointsDataFrame(coords = xy, data = background_all, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
head(background_all_sp)
```

@@

    }
}
write.csv(background_all_sp, "../output/bio/background_complete.csv", row.names = FALSE)
background_all <- as.data.frame(background_all_sp)
head(background_all)
```

>>>>

First you need to create columns for the data to be added to

```{r}
background_all$temp_depth <- NA
background_all$temp_surface <- NA
background_all$salinity_depth <- NA
background_all$salinity_surface <- NA
background_all$chl_depth <- NA
background_all$chl_surface <- NA
background_all$o2_depth <- NA
background_all$o2_surface <- NA
background_all$mlp_surface <- NA
background_all$ssh_surface <- NA
```

Second you need to put the background (background_all) into a spatialpointsdataframe.
```{r}
xy <- background_all[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude
background_all_sp <- SpatialPointsDataFrame(coords = xy, data = background_all, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
head(background_all_sp)
```

background_all <- read.csv("./output/bio/background_all_lonlat_nafo2_sciname_amo_nao_depthname_bath_cellobs.csv", header = TRUE

XXXXXXXXXXX split
```{r}
background_all2 <- background_all[background_all$year == 1999, ]
xy <- background_all2[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude
background_all_sp <- SpatialPointsDataFrame(coords = xy, data = background_all2, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
head(background_all_sp)
```

@@

    }
}
write.csv(background_all_sp, "../output/bio/background_complete_1999.csv", row.names = FALSE)
#background_all <- as.data.frame(background_all_sp)
head(background_all_sp)
```
